\documentclass[10pt,letterpaper]{article}

\usepackage{geometry}
\geometry{top=0.75in, bottom=0.75in, left=0.9in, right=0.9in}

\usepackage{amsmath}
\usepackage{booktabs}
\usepackage{xcolor}
\usepackage{microtype}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{titlesec}
\usepackage{tabularx}
\usepackage{mdframed}
\usepackage{multicol}

\definecolor{accent}{RGB}{20,60,120}
\definecolor{tier1}{RGB}{20,60,120}
\definecolor{tier2}{RGB}{40,110,80}
\definecolor{tier3}{RGB}{140,60,20}
\definecolor{lightgray}{RGB}{245,245,245}

\titleformat{\section}{\normalsize\bfseries\color{accent}}{}{0em}{}[\color{accent}\titlerule]
\titleformat{\subsection}{\small\bfseries\color{accent}}{}{0em}{}
\titlespacing{\section}{0pt}{8pt}{3pt}
\titlespacing{\subsection}{0pt}{4pt}{2pt}

\setlength{\parindent}{0pt}
\setlength{\parskip}{3pt}
\setlist[itemize]{leftmargin=1.2em, itemsep=1pt, topsep=2pt, parsep=0pt}
\setlist[enumerate]{leftmargin=1.5em, itemsep=1pt, topsep=2pt, parsep=0pt}

\hypersetup{colorlinks=true, urlcolor=accent, hidelinks}
\pagestyle{empty}

% ─────────────────────────────────────────────────────────────────────────────
\begin{document}

\begin{center}
{\large\bfseries\color{accent} Unified Tensor Systems — Licensing Target List}\\[3pt]
{\small Regime-Aware Spectral Acceleration · Patent Pending · \texttt{yoonikolas@gmail.com}}
\end{center}
\vspace{2pt}
\noindent\color{accent}\rule{\linewidth}{1pt}
\vspace{4pt}

% ── ASSET SUMMARY ─────────────────────────────────────────────────────────────
\begin{mdframed}[backgroundcolor=lightgray, linecolor=accent, linewidth=0.8pt,
  innerleftmargin=8pt, innerrightmargin=8pt, innertopmargin=5pt, innerbottommargin=5pt]
\textbf{Asset:} IEEE 39-bus CCT method — \textbf{57,946$\times$ faster} than RK4,
$<$2.73\% error, patent pending.
\quad\textbf{Format:} Licensing engine / API / plugin integration.
\quad\textbf{Outreach:} Attach investor brief PDF. No repo link.
\end{mdframed}

\vspace{4pt}

\begin{multicols}{2}

% ─────────────────────────────────────────────────────────────────────────────
\section*{\color{tier1}Tier 1 — Simulation Platform Vendors}
{\small\textit{Integrate the acceleration layer into existing tools.
 Highest leverage: reaches all end users.}}

\subsection*{Siemens Energy — PSS/E}
Industry standard for power flow and stability.\\
\textbf{Contact:} Power Systems Software division\\
\textbf{Pitch:} Drop-in CCT acceleration for PSS/E stability studies

\subsection*{GE Vernova — PSLF}
Power System Load Flow, used by major utilities.\\
\textbf{Contact:} Grid Software product group\\
\textbf{Pitch:} Spectral stability pre-screen before PSLF full integration

\subsection*{DigSILENT — PowerFactory}
Dominant in European markets, growing in North America.\\
\textbf{Contact:} \texttt{info@digsilent.de}\\
\textbf{Pitch:} Fast contingency ranking module for PowerFactory workflows

\subsection*{PowerWorld Corporation}
Power flow + stability, academic and utility market.\\
\textbf{Contact:} \texttt{sales@powerworld.com}\\
\textbf{Pitch:} Embedded CCT estimation in Simulator

\subsection*{Manitoba Hydro International — PSCAD}
Leading EMT simulation platform.\\
\textbf{Contact:} MHI business development\\
\textbf{Pitch:} Stability pre-screening complement to EMT simulation

\subsection*{ETAP (Operation Technology)}
Electrical system analysis for industrial + utility.\\
\textbf{Contact:} \texttt{info@etap.com}\\
\textbf{Pitch:} Fast transient stability module for ETAP platform

\vspace{4pt}
\columnbreak

% ─────────────────────────────────────────────────────────────────────────────
\section*{\color{tier2}Tier 2 — Grid Analytics \& Engineering Firms}
{\small\textit{Consulting firms that build custom stability tools for operators.}}

\subsection*{Quanta Technology}
Power grid consulting, Raleigh NC.\\
\textbf{Pitch:} License method for client N-1 screening engagements

\subsection*{EPRI (Electric Power Research Institute)}
Palo Alto CA — research licensing, utility consortium.\\
\textbf{Pitch:} Joint research program, EPRI report, member distribution

\subsection*{Hitachi Energy (formerly ABB Power Grids)}
Grid automation + stability analytics.\\
\textbf{Contact:} Grid software / digital energy division\\
\textbf{Pitch:} Integration into Hitachi PSSE or Neplan platform

\subsection*{Nexant}
Grid consulting, project finance analytics.\\
\textbf{Pitch:} Embedded CCT tool for renewable interconnection studies

% ─────────────────────────────────────────────────────────────────────────────
\section*{\color{tier3}Tier 3 — ISO/RTOs}
{\small\textit{Run N-1 analysis continuously. Direct operational need.}}

\begin{tabular}{ll}
\textbf{MISO}   & Carmel, IN — 15 states \\
\textbf{PJM}    & Norristown, PA — 13 states \\
\textbf{CAISO}  & Folsom, CA — California \\
\textbf{ERCOT}  & Taylor, TX — Texas \\
\textbf{ISO-NE} & Holyoke, MA — New England \\
\textbf{NYISO}  & Rensselaer, NY — New York \\
\end{tabular}

\textbf{Entry point:} Engineering / operations research contacts.\\
\textbf{Pitch:} Pilot on existing N-1 screening workflow.
Real-time contingency analysis feasibility study.

% ─────────────────────────────────────────────────────────────────────────────
\section*{Tier 4 — National Labs}
{\small\textit{Sponsored research, DOE funding, co-invention potential.}}

\begin{itemize}
  \item \textbf{NREL} (Golden, CO) — renewable integration stability
  \item \textbf{PNNL} (Richland, WA) — grid modernization, Koopman methods
  \item \textbf{ANL} (Lemont, IL) — power systems mathematics
  \item \textbf{ORNL} (Oak Ridge, TN) — grid resilience
\end{itemize}
\textbf{Pitch:} Collaborative research agreement (CRADA).
Method expands their Koopman/spectral stability portfolio.

\end{multicols}

\noindent\color{accent}\rule{\linewidth}{0.6pt}

% ── CONTACT STRATEGY ──────────────────────────────────────────────────────────
\section*{Contact Strategy}

\begin{tabular}{@{}lp{12.5cm}@{}}
\toprule
\textbf{Step} & \textbf{Action} \\
\midrule
1 & Cold email: subject line \textit{``CCT computation 57,946$\times$ faster than RK4 — patent pending''} \\
2 & Attach investor brief PDF only. No repo link. Two sentences on the result. \\
3 & Offer: 30-min technical call + live notebook demo (\texttt{github.com/YoNiko2063/demo}) \\
4 & For vendors: propose evaluation license (90 days, one product integration) \\
5 & For labs/ISOs: propose pilot study or CRADA; reference provisional patent filing \\
\bottomrule
\end{tabular}

\vspace{4pt}
{\small\textit{Lead with Tier 1 (simulation vendors) — one integration deal reaches thousands of engineers.
 Run Tier 3 (ISOs) in parallel for direct operational validation.
 Tier 4 for funding runway and co-publication.}}

\vspace{5pt}
\noindent\color{accent}\rule{\linewidth}{0.6pt}\\[2pt]
{\small Patent Pending \quad|\quad \texttt{yoonikolas@gmail.com}}

\end{document}
